Clean 2015 Raw Data

### 2018-04-14 data-raw/README.Rmd
Cleanup data-raw README

# Dry season 2015 importing and cleaning

DS2015 data can be accessed using:

```{r, eval=FALSE}
load(system.file("extdata", "DS2015_Raw_22DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_35DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_49DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_62DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_83DAI.csv", package = "rice.awd.pests"))
```

@@

# Dry season 2016 importing and cleaning

The 2016 season raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:

```{r, eval=FALSE}
load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
```

>>>>

# 2015 experiment

@@

# 2016 experiment
